---
title: "Kaggle Final RMD"
author: "Bailey Kui, Christy Hui, Shirley Tang"
date: "Due Sunday, December 5, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Let's reset our data, clean up NAs, and then run models with NAs fully cleaned up.

``` {r}
heart.train <- read.csv("HDtrainNew.csv")
heart.test <- read.csv("HDtestNoYNew.csv")
heart.train[which(heart.train == "F", arr.ind = TRUE)] <- "Female"
heart.train[which(heart.train == "M", arr.ind = TRUE)] <- "Male"
heart.test[which(heart.test == "F", arr.ind = TRUE)] <- "Female"
heart.test[which(heart.test == "M", arr.ind = TRUE)] <- "Male"
heart.train <- heart.train[, -1]
heart.test <- heart.test[, -1]
heart.train[which(is.na(heart.train$smoking_status)), 18] <- "Unknown"
heart.test[which(is.na(heart.test$smoking_status)), 18] <- "Unknown"
for (i in 1:4220){
  if(heart.train$Cholesterol[i] == 0) {
    heart.train$Cholesterol[i] <- mean(heart.train$Cholesterol)
  }
}

for (i in 1:4220){
  if(heart.train$RestingBP[i] == 0) {
    heart.train$RestingBP[i] <- mean(heart.train$RestingBP)
  }
}

table(heart.train$ever_married) # Yes is most often
for (i in 1:4220){
  if(is.na(heart.train$ever_married[i])) {
    heart.train$ever_married[i] <- "Yes"
  }
}

table(heart.train$work_type) # works is most often
for (i in 1:4220){
  if(is.na(heart.train$work_type[i])) {
    heart.train$work_type[i] <- "works"
  }
}

table(heart.train$Residence_type) # Urban is most often
for (i in 1:4220){
  if(is.na(heart.train$Residence_type[i])) {
    heart.train$Residence_type[i] <- "Urban"
  }
}

for (i in 1:1808){
  if(heart.test$Cholesterol[i] == 0) {
    heart.test$Cholesterol[i] <- mean(heart.test$Cholesterol)
  }
}

for (i in 1:1808){
  if(heart.test$RestingBP[i] == 0) {
    heart.test$RestingBP[i] <- mean(heart.test$RestingBP)
  }
}

table(heart.test$ever_married)
for (i in 1:1808){
  if(is.na(heart.test$ever_married[i])) {
    heart.test$ever_married[i] <- "Yes"
  }
}

table(heart.test$work_type)
for (i in 1:1808){
  if(is.na(heart.test$work_type[i])) {
    heart.test$work_type[i] <- "works"
  }
}

table(heart.test$Residence_type)
for (i in 1:1808){
  if(is.na(heart.test$Residence_type[i])) {
    heart.test$Residence_type[i] <- "Urban"
  }
}
```

## EDA: numerical

## Matrix plot
```{r}
# read in training dataset
HDtrain <- read.csv("HDtrainNew.csv")

library(corrplot)
library(GGally)
library(ggplot2)
library(gridExtra)

# numerical: Age, RestingBP, Cholesterol, MaxHR, Oldpeak, avg_glucose_level, bmi
vars <- data.frame(HDtrain["Age"], HDtrain["RestingBP"], HDtrain["Cholesterol"], HDtrain["MaxHR"], HDtrain["Oldpeak"], HDtrain["avg_glucose_level"], HDtrain["bmi"])
ggpairs(vars) # matrix plot
```

## Density plot

```{r}
# density plots for numerical predictors based on HeartDisease
# Age, RestingBP, Cholesterol, MaxHR, Oldpeak, avg_glucose_level, bmi
g1 <- ggplot(HDtrain, aes(x = Age)) + geom_density(aes(color = HeartDisease))
g2 <- ggplot(HDtrain, aes(x = RestingBP)) + geom_density(aes(color = HeartDisease))
g3 <- ggplot(HDtrain, aes(x = Cholesterol)) + geom_density(aes(color = HeartDisease))
g4 <- ggplot(HDtrain, aes(x = MaxHR)) + geom_density(aes(color = HeartDisease))
g5 <- ggplot(HDtrain, aes(x = Oldpeak)) + geom_density(aes(color = HeartDisease))
g6 <- ggplot(HDtrain, aes(x = avg_glucose_level)) + geom_density(aes(color = HeartDisease))
g7 <- ggplot(HDtrain, aes(x = bmi)) + geom_density(aes(color = HeartDisease))
grid.arrange(g1, g2, g3, g4, g5, g6, g7, nrow=4)
```

## EDA: categorical

```{r}
# stacked bar chart of Sex variable, demonstrating differing levels that need to be recoded
b1 <- ggplot(HDtrain, aes(x = Sex, fill = HeartDisease)) + geom_bar()
b1
```

## Now we prep for LDA, QDA, and KNN

``` {r}
# scale
heart.train$Age = scale(heart.train$Age)
heart.train$RestingBP = scale(heart.train$RestingBP)
heart.train$Cholesterol = scale(heart.train$Cholesterol)
heart.train$MaxHR = scale(heart.train$MaxHR)
heart.train$Oldpeak = scale(heart.train$Oldpeak)
heart.train$avg_glucose_level = scale(heart.train$avg_glucose_level)
heart.train$bmi = scale(heart.train$bmi)
```

## Try a GLM model and see what predictors are now significant

``` {r}
summary(glm(as.factor(heart.train$HeartDisease) ~ .,
            family = binomial(), data = heart.train))
```

## Let's try regsubsets and see what are our top 10 predictors will be

``` {r}
library(leaps)
subby.forward = regsubsets(as.factor(HeartDisease) ~., data = heart.train, nvmax = 19, method = "forward")
summary(subby.forward)
```

``` {r}
library(leaps)
subby.backward = regsubsets(as.factor(HeartDisease) ~., data = heart.train, nvmax = 19, method = "backward")
summary(subby.backward)
```

## Try LDAs Model with 6-10 predictors 

### First try 10 predictors without CV

``` {r}
library(MASS)
library(caret)
HD.lda10 = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType + ever_married,
             data = heart.train)
pred.HD.lda10.train = predict(HD.lda10, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.lda10.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.lda10.cv = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType + ever_married,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.lda10.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 9 predictors without CV

``` {r}
library(MASS)
library(caret)
HD.lda9 = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType,
             data = heart.train)
pred.HD.lda9.train = predict(HD.lda9, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.lda9.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.lda9.cv = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.lda9.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 8 predictors without CV

``` {r}
library(MASS)
library(caret)
HD.lda8 = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol,
             data = heart.train)
pred.HD.lda8.train = predict(HD.lda8, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.lda8.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.lda8.cv = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.lda8.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 7 predictors without CV

``` {r}
library(MASS)
library(caret)
HD.lda7 = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS,
             data = heart.train)
pred.HD.lda7.train = predict(HD.lda7, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.lda7.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.lda7.cv = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.lda7.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 6 predictors without CV

``` {r}
library(MASS)
library(caret)
HD.lda6 = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope,
             data = heart.train)
pred.HD.lda6.train = predict(HD.lda6, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.lda6.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.lda6.cv = lda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.lda6.cv$class),
                as.factor(heart.train$HeartDisease))
```


## Try QDAs Model with 6-10 predictors 

### Now try 10 predictors without CV

``` {r}
HD.qda10 = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType + ever_married,
             data = heart.train)
pred.HD.qda10.train = predict(HD.qda10, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.qda10.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.qda10.cv = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType + ever_married,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.qda10.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 9 predictors without CV

``` {r}
HD.qda9 = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType,
             data = heart.train)
pred.HD.qda9.train = predict(HD.qda9, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.qda9.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.qda9.cv = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.qda9.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 8 predictors without CV

``` {r}
HD.qda8 = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol,
             data = heart.train)
pred.HD.qda8.train = predict(HD.qda8, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.qda8.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.qda8.cv = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.qda8.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 7 predictors without CV

``` {r}
HD.qda7 = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS,
             data = heart.train)
pred.HD.qda7.train = predict(HD.qda7, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.qda7.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.qda7.cv = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.qda7.cv$class),
                as.factor(heart.train$HeartDisease))
```

### Now try 6 predictors without CV

``` {r}
HD.qda6 = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope,
             data = heart.train)
pred.HD.qda6.train = predict(HD.qda6, newdata = heart.train)
confusionMatrix(as.factor(pred.HD.qda6.train$class),
                as.factor(heart.train$HeartDisease))
```

### Try LOOCV

``` {r}
HD.qda6.cv = qda(as.factor(HeartDisease) ~ Oldpeak + avg_glucose_level + MaxHR + stroke + ExerciseAngina + ST_Slope + FastingBS + Cholesterol + ChestPainType + ever_married,
             data = heart.train,
             CV = TRUE)
confusionMatrix(as.factor(HD.qda7.cv$class),
                as.factor(heart.train$HeartDisease))
```

## Try KNN with varying levels of K

``` {r}
library(class)
HD.knn3 = knn(heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, 20],
              k = 3)
confusionMatrix(as.factor(HD.knn3), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn5 = knn(heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, 20],
              k = 5)
confusionMatrix(as.factor(HD.knn5), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn7 = knn(heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, 20],
              k = 7)
confusionMatrix(as.factor(HD.knn7), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn9 = knn(heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, 20],
              k = 9)
confusionMatrix(as.factor(HD.knn9), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn11 = knn(heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, 20],
              k = 11)
confusionMatrix(as.factor(HD.knn11), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn13 = knn(heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, c(2, 4, 5, 8, 10, 16, 17)], 
              heart.train[, 20],
              k = 13)
confusionMatrix(as.factor(HD.knn13), as.factor(heart.train[, 20]))
```

## Try LOOCV KNN with varying levels of K

``` {r}
library(class)
HD.knn3.cv = knn.cv(heart.train[, c(2, 4, 5, 8, 10, 16, 17)],
                    heart.train[, 20],
                    k = 3)
confusionMatrix(as.factor(HD.knn3.cv), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn5.cv = knn.cv(heart.train[, c(2, 4, 5, 8, 10, 16, 17)],
                    heart.train[, 20],
                    k = 5)
confusionMatrix(as.factor(HD.knn5.cv), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn7.cv = knn.cv(heart.train[, c(2, 4, 5, 8, 10, 16, 17)],
                    heart.train[, 20],
                    k = 7)
confusionMatrix(as.factor(HD.knn7.cv), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn9.cv = knn.cv(heart.train[, c(2, 4, 5, 8, 10, 16, 17)],
                    heart.train[, 20],
                    k = 9)
confusionMatrix(as.factor(HD.knn9.cv), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn11.cv = knn.cv(heart.train[, c(2, 4, 5, 8, 10, 16, 17)],
                     heart.train[, 20],
                     k = 11)
confusionMatrix(as.factor(HD.knn11.cv), as.factor(heart.train[, 20]))
```

``` {r}
library(class)
HD.knn13.cv = knn.cv(heart.train[, c(2, 4, 5, 8, 10, 16, 17)],
                     heart.train[, 20],
                     k = 13)
confusionMatrix(as.factor(HD.knn13.cv), as.factor(heart.train[, 20]))
```

## Find Accuracy Rates and Plot

### LDA

``` {r}
lda.misclass = c(mean(pred.HD.lda10.train$class != heart.train$HeartDisease),
                 mean(pred.HD.lda9.train$class != heart.train$HeartDisease),
                 mean(pred.HD.lda8.train$class != heart.train$HeartDisease),
                 mean(pred.HD.lda7.train$class != heart.train$HeartDisease),
                 mean(pred.HD.lda6.train$class != heart.train$HeartDisease))
qplot(c(10, 9, 8, 7, 6), lda.misclass, xlab = "No. of Predictors", ylab = "LDA Misclassification Rate")

1-mean(pred.HD.lda10.train$class != heart.train$HeartDisease)
1-mean(pred.HD.lda9.train$class != heart.train$HeartDisease)
1-mean(pred.HD.lda8.train$class != heart.train$HeartDisease)
1-mean(pred.HD.lda7.train$class != heart.train$HeartDisease)
1-mean(pred.HD.lda6.train$class != heart.train$HeartDisease)
```

``` {r}
lda.cv.misclass = c(mean(HD.lda10.cv$class != heart.train$HeartDisease),
                    mean(HD.lda9.cv$class != heart.train$HeartDisease),
                    mean(HD.lda8.cv$class != heart.train$HeartDisease),
                    mean(HD.lda7.cv$class != heart.train$HeartDisease),
                    mean(HD.lda6.cv$class != heart.train$HeartDisease))
qplot(c(10, 9, 8, 7, 6), lda.cv.misclass, xlab = "No. of Predictors", ylab = "LDA LOOCV Misclassification Rate")

1-mean(HD.lda10.cv$class != heart.train$HeartDisease)
1-mean(HD.lda9.cv$class != heart.train$HeartDisease)
1-mean(HD.lda8.cv$class != heart.train$HeartDisease)
1-mean(HD.lda7.cv$class != heart.train$HeartDisease)
1-mean(HD.lda6.cv$class != heart.train$HeartDisease)
```

### QDA

``` {r}
qda.misclass = c(mean(pred.HD.qda10.train$class != heart.train$HeartDisease),
                 mean(pred.HD.qda9.train$class != heart.train$HeartDisease),
                 mean(pred.HD.qda8.train$class != heart.train$HeartDisease),
                 mean(pred.HD.qda7.train$class != heart.train$HeartDisease),
                 mean(pred.HD.qda6.train$class != heart.train$HeartDisease))
qplot(c(10, 9, 8, 7, 6), qda.misclass, xlab = "No. of Predictors", ylab = "QDA Misclassification Rate")
1-mean(pred.HD.qda10.train$class != heart.train$HeartDisease)
1-mean(pred.HD.qda9.train$class != heart.train$HeartDisease)
1-mean(pred.HD.qda8.train$class != heart.train$HeartDisease)
1-mean(pred.HD.qda7.train$class != heart.train$HeartDisease)
1-mean(pred.HD.qda6.train$class != heart.train$HeartDisease)

```

``` {r}
qda.cv.misclass = c(mean(HD.qda10.cv$class != heart.train$HeartDisease),
                    mean(HD.qda9.cv$class != heart.train$HeartDisease),
                    mean(HD.qda8.cv$class != heart.train$HeartDisease),
                    mean(HD.qda7.cv$class != heart.train$HeartDisease),
                    mean(HD.qda6.cv$class != heart.train$HeartDisease))
qplot(c(10, 9, 8, 7, 6), qda.cv.misclass, xlab = "No. of Predictors", ylab = "QDA LOOCV Misclassification Rate")

1-mean(HD.qda10.cv$class != heart.train$HeartDisease)
1-mean(HD.qda9.cv$class != heart.train$HeartDisease)
1-mean(HD.qda8.cv$class != heart.train$HeartDisease)
1-mean(HD.qda7.cv$class != heart.train$HeartDisease)
1-mean(HD.qda6.cv$class != heart.train$HeartDisease)
```

### KNN

``` {r}
1-mean(HD.knn3 != heart.train$HeartDisease)
1-mean(HD.knn5 != heart.train$HeartDisease)
1-mean(HD.knn7 != heart.train$HeartDisease)
1-mean(HD.knn9 != heart.train$HeartDisease)
1-mean(HD.knn11 != heart.train$HeartDisease)
1-mean(HD.knn13 != heart.train$HeartDisease)
```

```{r}
1-mean(HD.knn3.cv != heart.train$HeartDisease)
1-mean(HD.knn5.cv != heart.train$HeartDisease)
1-mean(HD.knn7.cv != heart.train$HeartDisease)
1-mean(HD.knn9.cv != heart.train$HeartDisease)
1-mean(HD.knn11.cv != heart.train$HeartDisease)
1-mean(HD.knn13.cv != heart.train$HeartDisease)
```

## The below problems were done without scaling. Thus, we reread the file and reperform loops.

``` {r}
heart.train <- read.csv("HDtrainNew.csv")
heart.test <- read.csv("HDtestNoYNew.csv")
heart.train[which(heart.train == "F", arr.ind = TRUE)] <- "Female"
heart.train[which(heart.train == "M", arr.ind = TRUE)] <- "Male"
heart.test[which(heart.test == "F", arr.ind = TRUE)] <- "Female"
heart.test[which(heart.test == "M", arr.ind = TRUE)] <- "Male"
heart.train <- heart.train[, -1]
heart.test <- heart.test[, -1]
heart.train[which(is.na(heart.train$smoking_status)), 18] <- "Unknown"
heart.test[which(is.na(heart.test$smoking_status)), 18] <- "Unknown"
for (i in 1:4220){
  if(heart.train$Cholesterol[i] == 0) {
    heart.train$Cholesterol[i] <- mean(heart.train$Cholesterol)
  }
}

for (i in 1:4220){
  if(heart.train$RestingBP[i] == 0) {
    heart.train$RestingBP[i] <- mean(heart.train$RestingBP)
  }
}

table(heart.train$ever_married) # Yes is most often
for (i in 1:4220){
  if(is.na(heart.train$ever_married[i])) {
    heart.train$ever_married[i] <- "Yes"
  }
}

table(heart.train$work_type) # works is most often
for (i in 1:4220){
  if(is.na(heart.train$work_type[i])) {
    heart.train$work_type[i] <- "works"
  }
}

table(heart.train$Residence_type) # Urban is most often
for (i in 1:4220){
  if(is.na(heart.train$Residence_type[i])) {
    heart.train$Residence_type[i] <- "Urban"
  }
}

for (i in 1:1808){
  if(heart.test$Cholesterol[i] == 0) {
    heart.test$Cholesterol[i] <- mean(heart.test$Cholesterol)
  }
}

for (i in 1:1808){
  if(heart.test$RestingBP[i] == 0) {
    heart.test$RestingBP[i] <- mean(heart.test$RestingBP)
  }
}

table(heart.test$ever_married)
for (i in 1:1808){
  if(is.na(heart.test$ever_married[i])) {
    heart.test$ever_married[i] <- "Yes"
  }
}

table(heart.test$work_type)
for (i in 1:1808){
  if(is.na(heart.test$work_type[i])) {
    heart.test$work_type[i] <- "works"
  }
}

table(heart.test$Residence_type)
for (i in 1:1808){
  if(is.na(heart.test$Residence_type[i])) {
    heart.test$Residence_type[i] <- "Urban"
  }
}
```

## Random Forest

```{r}
library(randomForest)
set.seed(1128)
P.RFall <- randomForest(as.factor(HeartDisease) ~ ., data = heart.train, ntree = 100, mtry = 4, importantce = TRUE, nodesize = 2)

varImpPlot(P.RFall)

pred.RF <- predict(P.RFall, heart.train[,-20], type = "class")
table(heart.train[, 20], pred.RF)
pred.RF.test <- predict(P.RFall, heart.test, type = "class")
new5 <- data.frame(Ob = c(1:1808), HeartDisease = pred.RF.test)
write.csv(new5, "bkui_RF3.csv", row.names = FALSE)
```

## Logistic Regression

```{r}
HD.glm <- glm(as.factor(heart.train$HeartDisease) ~ .,
              family = binomial(), data = heart.train)
summary(HD.glm)

heart.train.best <- heart.train[, c(1, 3, 5, 6, 8, 9, 10, 16, 19, 20)]
HD.glm.best <- glm(as.factor(HeartDisease) ~ .,
                   family = binomial(), data = heart.train.best)
summary(HD.glm.best)
pred.HD.glm.train.best <- predict(HD.glm.best, heart.train.best, type = "response")
pred.HD.glm.train.best.out <- rep("No", 4220)
pred.HD.glm.train.best.out[pred.HD.glm.train.best > 0.524] <- "Yes"
table(heart.train$HeartDisease, pred.HD.glm.train.best.out) # confusion matrix
mean(pred.HD.glm.train.best.out != heart.train$HeartDisease) # misclassifcation rate

heart.test.best <- heart.test[, c(1, 3, 5, 6, 8, 9, 10, 16, 19)]
pred.HD.glm.test.best <- predict(HD.glm.best, heart.test.best, type = "response")
pred.HD.glm.test.best.out <- rep("No", 1808)
pred.HD.glm.test.best.out[pred.HD.glm.test.best > 0.524] <- "Yes"
df.best <- data.frame(Ob = c(1:1808), HeartDisease = pred.HD.glm.test.best.out)
write.csv(df.best, "bkui_glm_best.csv", row.names = FALSE)
```

## Logistic Regression ROCR

```{r}
library(ROCR)
pred <- prediction(pred.HD.glm.train.best, as.factor(heart.train$HeartDisease))
eval<- performance(pred,"acc")
plot(eval)
str(eval)
which.max(slot(eval,"y.values")[[1]])
acc<-slot(eval,"y.values")[[1]][which.max(slot(eval,"y.values")[[1]])]
acc
cut<- slot(eval,"x.values")[[1]][which.max(slot(eval,"y.values")[[1]])]
cut

a <- combn(c(1, 2, 3, 4, 5, 6, 8, 9, 10, 11, 13, 16, 18, 19), m = 9)
vec1 <- logical(0)
vec2 <- logical(0)
for (i in 1:ncol(a)){

# glm best predictors
heart.train.best <- heart.train[, c(a[,i], 20)]
HD.glm.best <- glm(as.factor(HeartDisease) ~ .,
family = binomial(), data = heart.train.best)
summary(HD.glm.best)

# glm best predictors training accuracy
pred.HD.glm.train.best <- predict(HD.glm.best, heart.train.best, type = "response")
pred <- prediction(pred.HD.glm.train.best, as.factor(heart.train$HeartDisease))
eval<- performance(pred,"acc")
b <- which.max(slot(eval,"y.values")[[1]])
vec1[i] <-slot(eval,"y.values")[[1]][b]
# vec2[i] <- slot(eval,"x.values")[[1]][b]
}
1 - max(vec1)
which(max(vec1) == vec1)
# vec2[which(max(vec1) == vec1)]
a[, which(max(vec1) == vec1)]

# glm best predictors
heart.train.best <- heart.train[, c(a[, which(max(vec1) == vec1)], 20)]
HD.glm.best <- glm(as.factor(HeartDisease) ~ .,
                   family = binomial(), data = heart.train.best)
summary(HD.glm.best)

# glm best predictors training accuracy
pred.HD.glm.train.best <- predict(HD.glm.best, heart.train.best, type = "response")
pred.HD.glm.train.best.out <- rep("No", 4220)
pred.HD.glm.train.best.out[pred.HD.glm.train.best > 0.5432] <- "Yes"
table(heart.train$HeartDisease, pred.HD.glm.train.best.out) # confusion matrix
mean(pred.HD.glm.train.best.out != heart.train$HeartDisease) # misclassifcation rate
# glm best predictors testing

heart.test.best <- heart.test[, c(a[, which(max(vec1) == vec1)])]
pred.HD.glm.test.best <- predict(HD.glm.best, heart.test.best, type = "response")
pred.HD.glm.test.best.out <- rep("No", 1808)
pred.HD.glm.test.best.out[pred.HD.glm.test.best > 0.5432] <- "Yes"
df.best <- data.frame(Ob = c(1:1808), HeartDisease = pred.HD.glm.test.best.out)
write.csv(df.best, "bkui_glm_best_ROCR.csv", row.names = FALSE)
```

## Tuning Parameter

```{r}
num <- seq(.4, .6, by = .0001)
rates <- logical(0)
for (i in 1:length(num)) {
  pred.HD.glm.train.best.out <- rep("No", 4220)
  pred.HD.glm.train.best.out[pred.HD.glm.train.best > num[i]] <- "Yes"
  rates[i] <- mean(pred.HD.glm.train.best.out != heart.train$HeartDisease)
}
which(min(rates) == rates)
num[which(min(rates) == rates)]
rates[which(min(rates) == rates)]
```




